Inferring cosmology from gravitational waves using non-parametric detector-frame mass distribution

### 2024-09-26 src/tex/ms.tex
[showyourwork] overleaf sync

\documentclass[sn-aps]{sn-jnl}

@@

We also mentioned a limitation of the method in Sec.~\ref{sec:inference_multi}.
The runtime of the optimization procedure scales with the number of parameters.
To perform higher dimensional analysis, we need to study using, instead of $d_\mathrm{JS}$, other distance measures that allow for faster optimization.
Either a distance measure that gives a simpler geometry to be optimized or a distance measure that can be calculated faster will be useful.
Other optimization algorithms should also be considered to allow for higher dimensional analysis and faster runtime.

>>>>

\documentclass[sn-aps, pdflatex]{sn-jnl}

@@
